### 2022-01-12 draft.tex
Deploying to gh-pages from @ PoisotLab/ms_metaweb_perspectives@b956cdfb8cb77c73f025396391c1980c59c62c0c 🚀

Graph embedding is a varied family of machine learning techniques aiming
to transform nodes and edges into a vector space, usually of a lower
dimension, whilst maximally retaining key properties of the graph (Yan
et al., 2005). Ecological networks are an interesting candidate for the
widespread application of embeddings, as they tend to posess a shared
sstructural backbone (Mora et al., 2018), which hints at structural
invariants that can be revealed a lower dimensions. Indeed, previous
work by Eklöf et al. (2013) suggests that food webs are inherently
low-dimensional objects, and can be adequately represented with less
than ten dimensions.

The popularity of graph embedding techniques in machine learning is
rather intuitive: while graphs are discrete objects, machine learning
techniques tend to handle continuous data better. Therefore, bringing a
discrete graph into a continuous vector space opens up a broader variety
of predictive algorithms.

@@

>>>>

Graph embedding is a varied family of machine learning techniques aiming
to transform nodes and edges into a vector space, usually of a lower
dimension, whilst maximally retaining key properties of the graph (Yan
et al., 2005). Ecological networks are an interesting candidate for the
widespread application of embeddings, as they tend to posess a shared
sstructural backbone (Mora et al., 2018), which hints at structural
invariants that can be revealed a lower dimensions. Indeed, previous
work by Eklöf et al. (2013) suggests that food webs are inherently
low-dimensional objects, and can be adequately represented with less
than ten dimensions. Simulation results by Botella et al. (2022) suggest
that there is no best method to identify architectural similarities
between networks, and that multiple approaches need to be tested and
compared to the network descriptor of interest.

But the popularity of graph embedding techniques in machine learning is
rather more intuitive than the search for structural invariants: while
graphs are discrete objects, machine learning techniques tend to handle
continuous data better. Therefore, bringing a discrete graph into a
continuous vector space opens up a broader variety of predictive
algorithms.

@@

\leavevmode\hypertarget{ref-Botella2022AppGra}{}%
Botella, C., Dray, S., Matias, C., Miele, V., \& Thuiller, W. (2022). An
appraisal of graph embeddings for comparing trophic network
architectures. \emph{Methods in Ecology and Evolution}, \emph{13}(1),
203--216. \url{https://doi.org/10.1111/2041-210X.13738}
